Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2016-03-15 Reviews/response.tex

\begin{quote}
    \begin{textit}
        {
        At the beginning of Section 3.1, the authors claim that if neither CCU
        is able to admit patients, then admission to the CCU is cancelled and
        the patient is admitted to a general ward. In my experience modelling
        CCUs, it is highly unlikely that a critical patient would ever be
        admitted to a general ward.  CCU beds are almost always equipped with
        ventilators and ward beds never. I believe that more likely courses of
        action are:
        \begin{itemize}
         \item Sending the patient to another hospital's CCU.  This would be a CCU
           outside of the model.
         \item ``Bumping" a patient currently in the CCU to a ward bed, to free up
           a bed. This would normally be a patient who was nearly ready to be
           transferred to the ward anyway.
         \item Accommodating the patient in the hospital's post-anesthesia care
           unit (PACU), which sometimes functions as an overflow for the CCU.
        \end{itemize}
        I recommend that the authors consult with their stakeholders and
        correct this comment in their paper, if necessary.  This wouldn't have
        any impact on their model, but it is important to use the correct
        language.
        }
    \end{textit}
\end{quote}

\begin{itemize}
    \item List all of above as options but use first as most related to model.
\end{itemize}

\begin{quote}
    \begin{textit}
        {
        The axis labels on many of the graphs are in a very small font. The
        font size should be increased.
        }
    \end{textit}
\end{quote}

All axis labels have now got a bigger font. We appreciate this comment: if any
other aspects of the graphics could be improved we would be happy to make the
suggested changes.

@@

\begin{quote}
    \begin{textit}
        {
        The optimisation problem is shown as a figure (Figure 6). I suggest
        that this be separated from the text with a header such as
        ``Optimisation Problem" (much like a theorem).  Calling it a figure
        seems like a misnomer, and for me, actually made it harder to find.
        }
    \end{textit}
\end{quote}

This has been changed:

\begin{itemize}
    \item The figure has been changed to a section with a header as suggested.
    \item A label (3) has been added for easier reference throughout the text.
\end{itemize}

@@

\begin{quote}
    \begin{textit}
        {
        In Figure 7, the caption should state which points are \(f_NH\) and
        which are \(F_RG\).
        }
    \end{textit}
\end{quote}

This is a good point, we have clarified this by noting `crosses' and `diamonds' in plain text in the caption.

### 2016-03-15 Paper/paper.tex
Changing the opt to section + add legen to fig.

Based on the discussion above, the game theoretic model is presented as a synchronous optimisation problem shown in Figure \ref{model1}.

\begin{figure}[!htbp]
\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
$$\left(U_{h}-t\right)^2$$
\hspace{2cm}Subject to:
\begin{align}
0\leq & K_h \leq c_{h}\nonumber\\
&K_h \in  \mathbb{Z}\nonumber
\end{align}
\caption{The optimisation problem underlying the game}\label{model1}
\end{figure}

@@

If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash Equilibrium.

@@

\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.7\textwidth]{./Images/best_responses_ex_for_proof.pdf}
    \end{center}
    \caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
\end{figure}

This point of intersection corresponds to a Nash Equilibrium of Figure \ref{model1}.

@@

We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.

@@

The game theoretic model of Figure \ref{model1} is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}. For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$. For the purpose of this paper this is implemented in \cite{sage}.

>>>>

Based on the discussion above, the game theoretic model is presented as a
synchronous optimisation problem shown in the following optimisation problem.

\textbf{Optimisation problem.}

\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
$$\left(U_{h}-t\right)^2$$
\hspace{2cm}Subject to:
\begin{align}
0\leq & K_h \leq c_{h}\label{model1}\\
&K_h \in  \mathbb{Z}\nonumber
\end{align}

@@

If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of
(\ref{model1}) has at least one Nash Equilibrium.

@@

\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.7\textwidth]{./Images/best_responses_ex_for_proof.pdf}
    \end{center}
    \caption{Plots of $f_{\NH}(K_{\RG})$ (crosses) and $f_{\RG}(K_{\NH})$ (diamonds)}\label{exampleforproof}
\end{figure}

This point of intersection corresponds to a Nash Equilibrium of (\ref{model1}).

@@

We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of (\ref{model1}) (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.

@@

The game theoretic model of (\ref{model1}) is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}. For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$. For the purpose of this paper this is implemented in \cite{sage}.
